%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Twenty Seconds Resume/CV
% LaTeX Template
% Version 1.1 (8/1/17)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Carmine Spagnuolo (cspagnuolo@unisa.it) with major modifications by 
% Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[letterpaper]{twentysecondcv} % a4paper for A4

\input{personal}

\begin{document}


%----------------------------------------------------------------------------------------

\makeprofile % Print the sidebar

%----------------------------------------------------------------------------------------
%	 INTERESTS
%----------------------------------------------------------------------------------------

\section{Skills}

I have more than \textbf{nine years of professional experience}. I extensively worked with \textbf{Python}, \textbf{C\#}, \textbf{C++}, \textbf{C}, \textbf{Java}, \textbf{Rust} and \textbf{Coq} code. I have a mixed background of \\\textbf{industry} and \textbf{academia}.

I am comfortable working on \textbf{complex code bases} in large and small teams, and I quickly get used to new technologies. I can \textbf{analyze problems} and then design, implement, evaluate, document, and present my solutions.

I am \textbf{outgoing} and I \textbf{love working in teams}. Due to my game development background, I am used to collaborating with different professional figures (e.g., artists, designers, musicians) and I have an eye for \textbf{user experience}.\\

%----------------------------------------------------------------------------------------
%	 EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Experience}

\begin{twenty} % Environment for a list with descriptions
	\twentyitem{2022}{R\&D Intern.}{Bloomberg LP}{ I worked on accelerating SAT solving using GPUs (C++, CUDA).  }
	\twentyitem{2019-2022}{PhD Student.}{Max Planck Institute}{ I studied timeliness certifications with formal verification (COQ) and on trace-based schedulability analysis on Linux (C, Rust). I mentored three interns and published three papers. }
	\twentyitem{2016-2019}{Game developer.}{34BigThings}{ I worked with Unity3D (C\#) and Unreal Engine (C++) on single player and online multiplayer games shipped on Steam, PS4, XboxOne, Switch, and mobiles. I developed gameplays, AIs, dev tools and UIs.}
	\twentyitem{2015-2016}{Freelance Software Engineer.}{Teoresi, Choralia, Maserati}{ I built an interactive visualization software and a learning game using Unity3D (C\#). I shipped on mobile devices and browsers (JS). I managed one artist I hired and collaborated with another engineer. }
	\twentyitem{2013-2016}{Software engineer.}{R.O. srl}{
		I developed software solutions for glass processing factories. I started as a developer (C, C++, C\#, SQL) and later transitioned to planning new features and managing a small team ($\leq$ 4 people). }
\end{twenty}


%----------------------------------------------------------------------------------------
%	 EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}

\begin{twenty} % Environment for a list with descriptions
	\twentyitem{2019-2022}{Master in Computer Science.}{Technische Universität Kaiserslautern}{}
	\twentyitem{2016-2019}{Bachelor in Computer Science.}{Università degli studi di Torino}{}
	\twentyitem{2015-2016}{Game dev: Software Development}{Event Horizon School.}{}
	%\twentyitem{<dates>}{<title>}{<location>}{<description>}
\end{twenty}

%----------------------------------------------------------------------------------------
%	 OTHER INFORMATION
%----------------------------------------------------------------------------------------

\section{Projects and Publications}

\begin{twenty} % Environment for a list with descriptions
	\twentyitem{2021}{Poet - Automatic Proof Generation.}{Max Planck institute}{ 
		I developed a tool that yields a worst-case-scenario timing analysis of software. 
		%The results are proven correct by a machine-checked COQ proof script. 
		Poet's publication (I am the first author) has received the \textit{outstanding paper award} at ECRTS2022, a top-class conference for real-time systems. \\
		\scriptsize (\url{https://pure.mpg.de/rest/items/item_3391739_1/component/file_3391740/content})\normalfont 
	}
	\twentyitem{2018}{Fast Mobile Cycle (FMC) Framework and Toolkit.}{34BigThings}{ 
		I developed an open-source Unity3D framework that makes the creation of production-ready casual games extremely fast, paired by a Python toolkit to execute bulk operations on the FMC games.
		%With FMC, I, an artist, and a designer developed ten production-ready games within a month. 
		\\
		\scriptsize (\url{www.github.com/34OpenThings})\normalfont
	 }
	 \twentyitem{2017}{Razer Chroma in Unreal Engine 4.}{34BigThings}{ 
		I developed a framework that handles light effects on Razer's Chroma hardware that are coherent to what is happening in the game. This system is still used today in every 34BigThings game.	
		\\
	 	\scriptsize (\url{www.youtube.com/watch?v=AihLBrJBufk&ab_channel=34BigThings})\normalfont
	 }
\end{twenty}
%
%----------------------------------------------------------------------------------------
%	 SECOND PAGE EXAMPLE
%----------------------------------------------------------------------------------------
%
%\newpage % Start a new page
%
%\makeprofile % Print the sidebar
%
%\section{Other information}
%
%\subsection{Review}
%
%Alice approaches Wonderland as an anthropologist, but maintains a strong sense of noblesse oblige that comes with her class status. She has confidence in her social position, education, and the Victorian virtue of good manners. Alice has a feeling of entitlement, particularly when comparing herself to Mabel, whom she declares has a ``poky little house," and no toys. Additionally, she flaunts her limited information base with anyone who will listen and becomes increasingly obsessed with the importance of good manners as she deals with the rude creatures of Wonderland. Alice maintains a superior attitude and behaves with solicitous indulgence toward those she believes are less privileged.
%
%\section{Other information}
%
%\subsection{Review}
%
%Alice approaches Wonderland as an anthropologist, but maintains a strong sense of noblesse oblige that comes with her class status. She has confidence in her social position, education, and the Victorian virtue of good manners. Alice has a feeling of entitlement, particularly when comparing herself to Mabel, whom she declares has a ``poky little house," and no toys. Additionally, she flaunts her limited information base with anyone who will listen and becomes increasingly obsessed with the importance of good manners as she deals with the rude creatures of Wonderland. Alice maintains a superior attitude and behaves with solicitous indulgence toward those she believes are less privileged.
%
%----------------------------------------------------------------------------------------
\end{document} 
