\profilesection{About me}

I was born in Turin, Italy, and have been tinkering with computers for as long as I can remember.  

My background is a mixed-bag of software engineering and computer science research. 


I started working professionally in \textbf{2013}, writing software for \textbf{industrial} glass cutting \textbf{optimisation}. 

In \textbf{2016}, I entered the \textbf{videogame development} world. In the following years, I split my time between work and student life, obtaining a bachelor's degree (focus on \textbf{formal methods}), and contributed to five major game releases at 34BigThings.

Once graduated, I moved to Germany and started a \textbf{joint master's and Ph.D. program} at \textbf{Max Planck Institute}, working at the intersection of \textbf{real-time systems} and \textbf{formal verification}. 

By \textbf{2022} I had completed my Master's, first-authored a research paper, and completed a research internship at Bloomberg LP. I decided to suspend my Ph.D. and return to the industry. 

Following my matured passion for \textbf{robotics} and \textbf{AI}, I moved to London and joined \textbf{Wayve Ltd}, building autonomous driving technologies. 

\profilesection{Languages}

L'\textbf{italiano} è la mia lingua madre,

I am fluent in \textbf{English},

und ich spreche etwas \textbf{Deutsch}.

\profilesection{Trivia}

I love camping and traveling with my bike: I often do the two together • 
I usually risk it, if I believe I am right • 
I love to simplify • 
I often relax by walking on a tensioned rope • 
I play guitar and --- less successfully --- sing.
